Hierarchical storage management in user space for neuroimaging applications

### 2024-11-06 paper/sea-neuro/paper-neuro.tex
Change latex template

\documentclass[fleqn,10pt]{wlscirep}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lineno}
\usepackage[binary-units]{siunitx}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{xspace}
\usepackage{todonotes}

@@

\title{Hierarchical storage management in user space for neuroimaging applications}

\author{Val\'erie Hayot-Sasson}
\author{Tristan Glatard}
\affil{Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada}

\begin{abstract}

@@

	% Neuroimaging open-data initiatives have led to increased availability of large
  % scientific datasets. While these datasets are shifting the processing
  % bottleneck from compute-intensive to data-intensive, current standardized
  % analysis tools have yet to adopt strategies that mitigate the costs
  % associated with large data transfers. A major challenge in adapting neuroimaging
  % applications for data-intensive processing is that they must be entirely
  % rewritten. To facilitate data management for standardized neuroimaging tools, we
  % developed Sea, a library that intercepts and redirects application read and
  % write calls to minimize data transfer time. In this paper, we investigate the
  % performance of Sea on three preprocessing pipelines implemented using standard toolboxes (FSL,
  % SPM and AFNI), using three neuroimaging datasets of different sizes
  % (OpenNeuro's ds001545, PREVENT-AD and the HCP dataset) on two high-performance
  % computing clusters. Our results demonstrate that Sea provides large speedups (up to 32$\times$) when
  % the shared file system's (e.g. Lustre) performance is deteriorated. When the
  % shared file system is not overburdened by other users, performance is
  % unaffected by Sea, suggesting that Sea's overhead is minimal even in cases
  % where its benefits are limited. Overall, Sea is beneficial, even when performance gain
  % is minimal, as it can be used to limit the number of files created on parallel file systems.
\end{abstract}
\begin{document}

\flushbottom
\maketitle
%  Click the title above to edit the author information and abstract

\thispagestyle{empty}

@@

    \centering
    \includegraphics[width=\columnwidth]{figures/sea-diagram.pdf}%
\caption{The Sea data-management library overview}
\label{fig:seaneuro:diagram}
\end{figure*}
    Sea (Figure~\ref{fig:seaneuro:diagram}) is a data-management library that leverages
    the \texttt{LD\_PRELOAD}
    trick to intercept POSIX file system calls, or more specifically, file access calls to the GNU C library,
    glibc, on Linux systems. This enables Sea to redirect write calls
    aimed at slower storage devices to a faster device whenever possible.
    Similarly, when intercepting read calls, Sea can choose to read from a
    faster device if a copy is available on that device. Sea decides which
    storage location it can write to based on the details provided in an
    initialization file called \texttt{sea.ini}. This file informs Sea of which
    locations it can use to read and write to, and well as their order of
    priority. Importantly, Sea is not a filesystem, but rather a
    lightweight tool that redirects files to more optimal storage devices.

% \tristan{I find this section lacks a clear focus. What are the key points from
% these results? You should focus on them and possibly name your paragraphs
% accordingly, for improved clarity. My takeaways would be the following:
% \begin{enumerate} \item In controlled conditions, important speed-ups are
% observed. Mention min, average and max speed-up for all conditions. \item
% Speed-up is correlated with baseline makespan \item Other determinants of
% speed-up are unclear \item Overhead is minor \item Speed-ups are also observed
% in production cluster \end{enumerate}
% }
\begin{figure*}

\begin{subfigure}{0.5\textwidth}
    \centering
    \captionsetup{width=.85\linewidth}
    \includegraphics[width=\columnwidth]{figures/slashbin_nozoom.pdf}%
    \caption{Complete results}\label{fig:seaneuro:slashbinfull}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \centering
    \captionsetup{width=.85\linewidth}
    \includegraphics[width=\linewidth]{figures/slashbin_withzoom.pdf}
    \caption{Zoomed between 0 and 5000 seconds}\label{fig:seaneuro:slashbinzoom}
\end{subfigure}
\caption{Makespan comparison between Sea and Baseline on controlled dedicated cluster. Makespan
denotes the total time between execution launch and completion of the last computing task.}
\label{fig:seaneuro:slashbin}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.7\columnwidth]{figures/beluga_sea_tmpfs.pdf}%
\caption{Makespan comparison between Sea and tmpfs on the production cluster with flushing disabled}
\label{fig:seaneuro:tmpfs}
\end{figure*}

\begin{subfigure}{0.5\textwidth}
    \centering
    \captionsetup{width=.85\linewidth}
    \includegraphics[width=\columnwidth]{figures/beluga_withoutflush_nozoom.pdf}%
    \caption{Complete results}\label{fig:seaneuro:belugafull}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \centering
    \captionsetup{width=.85\linewidth}
    \includegraphics[width=\linewidth]{figures/beluga_withoutflush_zoom.pdf}
    \caption{Zoomed between 0 and 2000 seconds}\label{fig:seaneuro:belugazoom}
\end{subfigure}
\caption{Makespan comparison between Sea and Baseline on the production cluster with flushing disabled}
\label{fig:seaneuro:beluga-noflush}
\end{figure*}

\begin{figure*}
\begin{subfigure}{0.5\textwidth}
    \centering
    \captionsetup{width=.85\linewidth}
    \includegraphics[width=\columnwidth]{figures/beluga_withflush_nozoom.pdf}%
    \caption{Complete results}\label{fig:seaneuro:belugafullwf}
\end{subfigure}
\begin{subfigure}{0.5\textwidth}
    \centering
    \captionsetup{width=.85\linewidth}
    \includegraphics[width=\linewidth]{figures/beluga_withflush_zoom.pdf}
    \caption{Zoomed between 0 and 2000 seconds}\label{fig:seaneuro:belugazoomwf}
\end{subfigure}
\caption{Makespan comparison between Sea and Baseline on the production cluster with flushing enabled for all files}
\label{fig:seaneuro:beluga-wflush}
\end{figure*}

    \subsection{Conclusion and Future work}

    %Flushing - rely on modification time
    \section{Materials and Methods}

@@

@@

    \bibliography{biblio}

>>>>

\documentclass[utf8]{FrontiersinHarvard}
\usepackage{url,hyperref,lineno,microtype,subcaption}
\usepackage[onehalfspacing]{setspace}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lineno}
\usepackage[binary-units]{siunitx}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{xspace}
\usepackage{todonotes}

@@

%\title{Hierarchical storage management in user space for neuroimaging applications}

\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{V. Hayot-Sasson {et~al.}} %use et al only if is more than 1 author
\def\Authors{Val\'erie Hayot-Sasson\,$^{1,*}$ and Tristan Glatard\,$^{1}$}
% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
\def\Address{$^{1}$Department of Computer Science and Software Engineering, Concordia University, Montreal, Qu\'ebec, Canada}
% The Corresponding Author should be marked with an asterisk
% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
\def\corrAuthor{Corresponding Author}

\def\corrEmail{vhayot@uchicago.edu}
% \author{Val\'erie Hayot-Sasson}
% \author{Tristan Glatard}
% \affil{}

\begin{document}
    \onecolumn
    \firstpage{1}

  \title[Sea]{Hierarchical storage management in user space for neuroimaging applications}

  \author[\firstAuthorLast ]{\Authors} %This field will be automatically populated
  \address{} %This field will be automatically populated
  \correspondance{} 
  \extraAuth{}

  \maketitle
  \begin{abstract}

@@

	% Neuroimaging open-data initiatives have led to increased availability of large
  % scientific datasets. While these datasets are shifting the processing
  % bottleneck from compute-intensive to data-intensive, current standardized
  % analysis tools have yet to adopt strategies that mitigate the costs
  % associated with large data transfers. A major challenge in adapting neuroimaging
  % applications for data-intensive processing is that they must be entirely
  % rewritten. To facilitate data management for standardized neuroimaging tools, we
  % developed Sea, a library that intercepts and redirects application read and
  % write calls to minimize data transfer time. In this paper, we investigate the
  % performance of Sea on three preprocessing pipelines implemented using standard toolboxes (FSL,
  % SPM and AFNI), using three neuroimaging datasets of different sizes
  % (OpenNeuro's ds001545, PREVENT-AD and the HCP dataset) on two high-performance
  % computing clusters. Our results demonstrate that Sea provides large speedups (up to 32$\times$) when
  % the shared file system's (e.g. Lustre) performance is deteriorated. When the
  % shared file system is not overburdened by other users, performance is
  % unaffected by Sea, suggesting that Sea's overhead is minimal even in cases
  % where its benefits are limited. Overall, Sea is beneficial, even when performance gain
  % is minimal, as it can be used to limit the number of files created on parallel file systems.
\end{abstract}

% \flushbottom
% \maketitle
% %  Click the title above to edit the author information and abstract

% \thispagestyle{empty}

@@

    \section{Materials and Methods}

@@

    \centering
    \includegraphics[width=\columnwidth]{figures/sea-diagram.pdf}%
    \captionsetup{justification=centering}
    \captionof{figure}{The Sea data-management library overview}
    \label{fig:seaneuro:diagram}
\end{figure*}

    Sea (Figure~\ref{fig:seaneuro:diagram}) is a data-management library that leverages
    the \texttt{LD\_PRELOAD}
    trick to intercept POSIX file system calls, or more specifically, file access calls to the GNU C library,
    glibc, on Linux systems. This enables Sea to redirect write calls
    aimed at slower storage devices to a faster device whenever possible.
    Similarly, when intercepting read calls, Sea can choose to read from a
    faster device if a copy is available on that device. Sea decides which
    storage location it can write to based on the details provided in an
    initialization file called \texttt{sea.ini}. This file informs Sea of which
    locations it can use to read and write to, and well as their order of
    priority. Importantly, Sea is not a filesystem, but rather a
    lightweight tool that redirects files to more optimal storage devices.

% \tristan{I find this section lacks a clear focus. What are the key points from
% these results? You should focus on them and possibly name your paragraphs
% accordingly, for improved clarity. My takeaways would be the following:
% \begin{enumerate} \item In controlled conditions, important speed-ups are
% observed. Mention min, average and max speed-up for all conditions. \item
% Speed-up is correlated with baseline makespan \item Other determinants of
% speed-up are unclear \item Overhead is minor \item Speed-ups are also observed
% in production cluster \end{enumerate}
% }

%\setcounter{figure}{2}
%\setcounter{subfigure}{0}
\begin{subfigure}
%\setcounter{figure}{2}
%\setcounter{subfigure}{0}
    \centering
    \begin{minipage}[b]{0.5\textwidth}
      \centering
        \includegraphics[width=\linewidth]{figures/slashbin_nozoom.pdf}
        \captionsetup{justification=centering}
        \captionof{subfigure}{Complete results}\label{fig:seaneuro:slashbinfull}
    \end{minipage}%
    \begin{minipage}[b]{0.5\textwidth}
      \centering
        \includegraphics[width=\linewidth]{figures/slashbin_withzoom.pdf}
        \captionsetup{justification=centering}
        \captionof{subfigure}{Zoomed between 0 and 5000 seconds}\label{fig:seaneuro:slashbinzoom}
    \end{minipage}

%\setcounter{figure}{2}
\setcounter{subfigure}{-1}
    \caption{Makespan comparison between Sea and Baseline on controlled dedicated cluster. Makespan
    denotes the total time between execution launch and completion of the last computing task.}
    \label{fig:seaneuro:slashbin}
\end{subfigure}

% \begin{figure*}

% % \begin{subfigure}{0.5\textwidth}
%     \centering
%     \captionsetup{width=.85\linewidth}
%     \includegraphics[width=\columnwidth]{figures/slashbin_nozoom.pdf}%
%     \caption{Complete results}\label{fig:seaneuro:slashbinfull}
% % \end{subfigure}
% % \begin{subfigure}{0.5\textwidth}
% %     \centering
% %     \captionsetup{width=.85\linewidth}
% %     \includegraphics[width=\linewidth]{figures/slashbin_withzoom.pdf}
% %     \caption{Zoomed between 0 and 5000 seconds}\label{fig:seaneuro:slashbinzoom}
% % \end{subfigure}
% \caption{Makespan comparison between Sea and Baseline on controlled dedicated cluster. Makespan
% denotes the total time between execution launch and completion of the last computing task.}
% %\label{fig:seaneuro:slashbin}
% \end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.5\linewidth]{figures/beluga_sea_tmpfs.pdf}%
\caption{Makespan comparison between Sea and tmpfs on the production cluster with flushing disabled}
\label{fig:seaneuro:tmpfs}
\end{figure*}

\begin{subfigure}
  %\setcounter{figure}{2}
  %\setcounter{subfigure}{0}
      \centering
      \begin{minipage}[b]{0.5\textwidth}
        \centering
          \includegraphics[width=\linewidth]{figures/beluga_withoutflush_nozoom.pdf}
          \captionsetup{justification=centering}
          \captionof{subfigure}{Complete results}\label{fig:seaneuro:belugafull}
      \end{minipage}%
      \begin{minipage}[b]{0.5\textwidth}
        \centering
          \includegraphics[width=\linewidth]{figures/beluga_withoutflush_zoom.pdf}
          \captionsetup{justification=centering}
          \captionof{subfigure}{Zoomed between 0 and 2000 seconds}\label{fig:seaneuro:belugazoom}
      \end{minipage}

  %\setcounter{figure}{2}
  \setcounter{subfigure}{-1}
      \caption{Makespan comparison between Sea and Baseline on the production cluster with flushing disabled}
      \label{fig:seaneuro:beluga-noflush}
  \end{subfigure}

% \begin{figure*}

% % \begin{subfigure}{0.5\textwidth}
%     \centering
%     \captionsetup{width=.85\linewidth}
%     \includegraphics[width=\columnwidth]{figures/beluga_withoutflush_nozoom.pdf}%
%     \caption{Complete results}\label{fig:seaneuro:belugafull}
% % \end{subfigure}
% % \begin{subfigure}{0.5\textwidth}
% %     \centering
% %     \captionsetup{width=.85\linewidth}
% %     \includegraphics[width=\linewidth]{figures/beluga_withoutflush_zoom.pdf}
% %     \caption{Zoomed between 0 and 2000 seconds}\label{fig:seaneuro:belugazoom}
% % \end{subfigure}
% \caption{Makespan comparison between Sea and Baseline on the production cluster with flushing disabled}
% \label{fig:seaneuro:beluga-noflush}
% \end{figure*}

\begin{subfigure}
  %\setcounter{figure}{2}
  %\setcounter{subfigure}{0}
      \centering
      \begin{minipage}[b]{0.5\textwidth}
        \centering
          \includegraphics[width=\linewidth]{figures/beluga_withflush_nozoom.pdf}
          \captionsetup{justification=centering}
          \captionof{subfigure}{Complete results}\label{fig:seaneuro:belugafullwf}
      \end{minipage}%
      \begin{minipage}[b]{0.5\textwidth}
        \centering
          \includegraphics[width=\linewidth]{figures/beluga_withflush_zoom.pdf}
          \captionsetup{justification=centering}
          \captionof{subfigure}{Zoomed between 0 and 2000 seconds}\label{fig:seaneuro:belugazoomwf}
      \end{minipage}

  %\setcounter{figure}{2}
  \setcounter{subfigure}{-1}
      \caption{Makespan comparison between Sea and Baseline on the production cluster with flushing enabled for all files}
      \label{fig:seaneuro:beluga-wflush}
  \end{subfigure}

% \begin{figure*}
% %\begin{subfigure}{0.5\textwidth}
%     \centering
%     \captionsetup{width=.85\linewidth}
%     \includegraphics[width=\columnwidth]{figures/beluga_withflush_nozoom.pdf}%
%     \caption{Complete results}\label{fig:seaneuro:belugafullwf}
% % \end{subfigure}
% % \begin{subfigure}{0.5\textwidth}
% %     \centering
% %     \captionsetup{width=.85\linewidth}
% %     \includegraphics[width=\linewidth]{figures/beluga_withflush_zoom.pdf}
% %     \caption{Zoomed between 0 and 2000 seconds}\label{fig:seaneuro:belugazoomwf}
% % \end{subfigure}
% \caption{Makespan comparison between Sea and Baseline on the production cluster with flushing enabled for all files}
% \label{fig:seaneuro:beluga-wflush}
% \end{figure*}

    \section{Conclusion and Future work}

    %Flushing - rely on modification time

@@

    \bibliographystyle{Frontiers-Harvard}
    \bibliography{biblio}
